% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.55in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{ulem}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{url}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Rui Tian}}

6211 Sudikoff, Hanover, NH 03755\ \ \textbullet
\ \ +1(215)-350-8340\ \ \textbullet
\ \ +86-15195808380\ \ \textbullet
\ \ rui.tian.gr@dartmouth.edu\ \
\end{center}

\hrule
%\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

    \item
	\headerrow
		{\textbf{Master of Science in Computer Science (67\% Tuition waiver)}}
		{Aug. 2014 -- June 2016 (Expected)}
	\\
	\headerrow
        {Dartmouth College, Hanover, NH}
		

	\item
	\headerrow
		{\textbf{Master of Science in Electrical Engineering (Full funded by scholarship)}}
		{Aug. 2012 -- June 2014}
	\\
	\headerrow
		{Dartmouth College, Hanover, NH}
        {}
    \\
    \headerrow
        {Thesis: \textit{Micro-Fabrication and Circuit Optimization for Magnetic Components of High-Efficiency DC-DC Converters}}
		

	\item
	\headerrow
		{\textbf{Bachelor of Science in Material Physics}}
		{Sep. 2008 -- June 2012}
	\\
	\headerrow
		{Nanjing University, Nanjing, China}

\end{itemize}


%\hrule
%\vspace{-0.4em}
%\subsection*{Market Experience}
%
%\begin{itemize}
%	\parskip=0.1em
%
%	\item
%	\headerrow
%		{\textbf{Dartmouth Mini Hedge Fund}}
%		{\textbf{Hanover, NH}}
%	\\
%	\headerrow
%		{\emph{Chief Risk Officer}}
%		{\emph{Jan. 2013 -- present}}
%	\begin{itemize*}
%		\item Co-found a student-run fund focusing on trading foreign exchange.
%		\item Develop a scalable platform to back-test and real-time simulate trading strategies under C\#.
%        \item Develop and test quantitative trading strategies for both trending and ranging markets. Combined strategies reach 30.5\% annual return with 35.5\% max drawdown since data from 2008.
%        \item Paper-trade self-developed strategies on G10 currency markets. Gain 6.37\% return in three months.
%	\end{itemize*}
%
%\end{itemize}
\hrule
\vspace{-0.4em}
\subsection*{Skills}


\begin{itemize}
    \parskip=0.01em
     \item Proficient: Java, C, Python, C++, Android Programming and MATLAB; LaTeX, Git and SVN;
     \item Familiar: Linux Programming, SQL, CSS, JavaScript and HTML; Clojure;
     \item GitHub: \url{https://github.com/complete46}
\end{itemize}


\hrule
%\vspace{-0.4em}

\subsection*{Professional Experience}

\begin{itemize}
	%\parskip=0.1em

    \item
    \headerrow
		{\textbf{Software Developer Engineer Intern}}
		{\textbf{June. 2015 -- Sept. 2015 (Expected)}}
	\\
    \headerrow
		{Elastic Block Storage Team, Amazon Web Service}
		{Seattle, WA}
	\begin{itemize*}
        \item Participating in implementing a new generation of distributed system that provides extreme high overall on availability, consistency and performance. 
        \item Designing and developing test tools with Clojure and Jepson to verify implementation.
	\end{itemize*}

    \item
    \headerrow
		{\textbf{C Developer: DarySync}}
		{\textbf{Mar. 2015 -- May 2015}}
	\\
    \headerrow
		{Network Course Project, Computer Science Department, Dartmouth College}
		{Hanover, NH}
	\begin{itemize*}
        \item DartSync is a peer to peer based file synchronization system oriented towards Linux machines based on P2P protocol. It supports breakpoint resuming and partial downloading.
        \item Participated in implementing Tracker (cloud side) and Peer (user side). Independently implemented a directory monitor that supports file rename, subdirectory monitoring, user specified private files, plus common feature including adding, changing and deleting files in the monitoring folders.
	\end{itemize*}

    \item
    \headerrow
		{\textbf{Android Developer: MyRuns and DartmouthMining}}
		{\textbf{Jan. 2015 -- Mar. 2015}}
	\\
    \headerrow
		{Smartphone Programming Course, Computer Science Department, Dartmouth College}
		{Hanover, NH}
	\begin{itemize*}
        \item MyRuns: Developed and deployed an Android app to track and analyze the work out records of users by applying location tracking, activity recognition, Google App Engine and Google Cloud Message.
        \item DartmouthMining: Developed and deployed another Android app to mine the events around Dartmouth campus; Implemented a decision tree to classified acquired events and communication between users and cloud.
	\end{itemize*}

    \item
    \headerrow
		{\textbf{Project Leader: Breast Cancer Predication from Mammographic Findings}}
		{\textbf{Sept. 2014 -- Nov. 2014}}
	\\
    \headerrow
		{Machine Learning Course, Computer Science Department, Dartmouth College}
		{Hanover, NH}
	\begin{itemize*}
        \item Implemented a specified version of random forest algorithm for breast cancer prediction
        \item Parallelized the computation and improved the computation efficiency by a factor of 90.

	\end{itemize*}

%	\item
%	\headerrow
%		{\textbf{Research Assistant: Agile Delivery of Electrical Power Technology}}
%		{\textbf{Aug. 2012 -- June 2014}}
%	\\
%    \headerrow
%	    {Thayer Engineering School, Dartmouth College associated with MIT, UPenn and GeorgiaTech}
%		{Hanover, NH}
%	\begin{itemize*}
%        \item Worked on project "Agile Delivery of Electrical Power Technology" funded by U.S. Department of Energy (US-DOE, DE-FOA-0000288). Available at \url{https://arpa-e-foa.energy.gov}; Modeled and optimized circuit performances with both analytical and numerical analysis; implemented particular version of comprehensive learning particle swarm optimization
%
%	\end{itemize*}
\end{itemize}


\hrule
%\vspace{-0.4em}


\subsection*{Awards}

\begin{itemize}
	\parskip=0.1em
    \item
    \headerrow
    {Full Graduate Research Fellowship for Master Student at Dartmouth College (2 - 3 winners per year)}
    {2012 - 2014}

    \item
    \headerrow
    {Outstanding Undergraduate Scholarship at Nanjing University}
    {2009 \& 2010}

\end{itemize}

\hrule
%\vspace{-0.4em}

%\subsection*{Academic Publications}
%  \begin{itemize}
%    \parskip=0.1em
%    \item Harburg, Daniel V., Alex J. Hanson, Yue Song, Jizheng Qiu, \uline{Rui Tian}, Christopher G. Levey, Charles R.  Sullivan, and David Otten. "Measured performance and micro-fabrication of racetrack power inductors." In Energy Conversion Congress and Exposition (ECCE), 2013 IEEE, pp. 614-620. IEEE, 2013
%
%
%    \item Di Yao, Christopher G. Levey, \uline{Rui Tian} and Charles R. Sullivan. "Microfabricated V-Groove power inductors using multilayer Co-Zr-O thin films for very-high-frequency DC-DC converters." In Power Electronics, IEEE Transactions, Vol. 28, Issue 9, pp. 4384-4394. IEEE, 2013
%
%  \end{itemize}




\end{document}
